Kronos \& Krios: TBD

### 2017-05-26 paper/ms.tex
Use deluxetable and seperate file

\author{
  Semyeong Oh\altaffilmark{\pu,\lead},
  APW, JMB, KH, NL, DWH, DNS, JW
}

@@

\begin{abstract}
  We report and discuss the discovery of a co-moving pair of bright solar-type
  stars, \sunanalog\ and \bizarreone\, with significant differences in their chemical
  abundance patterns.
  The two stars are co-spatial ($|\Delta \bs{x}| < XX~\pc$) at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocities
  ($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence), as inferred from \gaia\
  \tgas\ proper motions and high resolution radial velocity measurements.
  Both stars are young with ages $\approx$$500~{\rm Myr}$ as estimated from
  their lithium abundances, favoring the idea that they were born together and
  are or were recently a bound, wide binary system.
  However, the metallicities and chemical abundances of refractory
  elements in the two stars are very different, challenging this simple picture.
  In order to reconcile the seemingly contradictory observations,
  we consider scenarios in which the pair is unrelated despite
  its current spatial and kinematic configuration, and
  those in which the pair formed together but may now have different chemistry.
  In the latter, we consider the possibility that the more metal-rich of the two,
  \bizarreone, accreted $\approx$10's of Earth masses of protoplanetary, rocky material,
  selectively enhancing the refractory elements.
  Direct-imaging and precision radial velocity follow-up to study the existence
  or properties of planetary systems around these stars would help distinguish
  these scenarios.
\end{abstract}

@@

Here, we report and discuss the discovery of a co-moving pair of solar twin stars,
HD~240430 and HD~240429, with unusual chemical abundance and differential abundance patterns
that strongly suggest a dramatic accretion of planetary material by the two stars.
We nickname the two stars \bizarreone\ (HD~240430) and
\sunanalog\ (HD~240429) throughout the \documentname.
\todo{section summary}

@@

Though previously recognized as a visual double star system
(\citealt{2001AJ....122.3466M}), \sunanalog\ and \bizarreone\ were identified as a
candidate co-moving star pair in our recent search for co-moving stars using the
proper motions and parallaxes from the \tgas catalog, a component of \gaia\ \dr\
(the astrometric measurements are listed in \tablename~\ref{tab:t2}).
We refer the readers to this previous work (\citealt{2016arXiv161202440O}) for a
full explanation of the methodology behind this search and only briefly describe
the method here.
For a given pair, we compute a marginalized likelihood ratio between the
hypotheses (1) that a given pair of stars share the same 3D velocity vector, and
(2) that they have independent 3D velocity vectors, both given only observations
of two components of the velocities (proper motions).
We then select a sample of high-confidence co-moving star pairs by making a
conservative cut on this likelihood ratio.
In the resulting catalog of co-moving pairs (\citealt{2016arXiv161202440O}),
the pair presented in this paper was assigned a group id of 1199,
and the marginalized likelihood ratio (Bayes factor)
between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
well above the adopted cut value of 6.
We have checked that we do not find any possible additional co-moving companions
by lowering the likelihood ratio cut for the stars around this pair.

In a separate effort to study detailed chemical abundances of
potential planet-hosting stars, \citet{2016ApJS..225...32B}
analyzed high resolution spectra of both stars obtained using HIRES spectrograph
on Keck~I telescope.
The spectral resolution is \todo{$R\approx XXX$} and the wavelength coverage is \todo{$XXX-XXX$~\AA}.
The resulting measurements include abundances measured for 15
chemical species (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as
well as high precision radial velocities.
Other stellar parameters derived from these spectra are included in
\tablename~\ref{tab:t2}.

Combining these precise radial velocities with the \gaia\ astrometry, we can
compare differences between the inferred 6D phase-space properties for the
two stars.
We start by generating posterior samples over the Heliocentric distance, $r$,
tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $\hat{v}_r$,
given the observed parallax, $\pi$, and proper motion components,
$(\mu_{\alpha^*}, \mu_\delta)$, and radial velocity, $v_r$.
By defining the vectors
% SMOH: I understand you meant hat v_r as the latent true radial velocity but
% personally think a) it can confuse some people that there are hat quantities
% with no-hat quantities for hat-y vector and thus b) it'd be better to use hat
% quantities for observed variables and no-hat for latent true ones.
% SMOH: v_r is missing in the LHS of eq(3)
\begin{eqnarray}
  \vec{y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          \pi &
          \mu_{\alpha^*} &
          \mu_\delta &
          v_r
        \end{array}
      \right)}\\
  \hat{\vec{y}} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          r^{-1} &
          r^{-1}\,v_\alpha &
          r^{-1}\,v_\delta &
          \hat{v}_r
        \end{array}
      \right)}
\end{eqnarray}
and by considering the covariance matrix $\mat{C}$ between the observed
quantities (provided by \tgas\ and extended to include the uncorrelated radial
velocity uncertainty), the likelihood can be written
\begin{eqnarray}
p(\pi, \mu_{\alpha^*}, \mu_\delta \given r, v_\alpha, v_\delta) &=&
  \left[\det\left(\frac{\mat{C}^{-1}}{2\pi}\right)\right]^{1/2} \,
    \exp \left[ -\frac{1}{2} \transp{\left(\vec{y} - \hat{\vec{y}} \right)} \,
    \mat{C}^{-1} \,
    \left(\vec{y} - \hat{\vec{y}} \right) \right] \label{eq:likefn} \quad .
\end{eqnarray}
We adopt a uniform space density prior for the distance and an isotropic
Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
\begin{eqnarray}
p(r) &=&
  \begin{cases}
    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
    0              & \text{otherwise}
  \end{cases}\\
p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
\end{eqnarray}
For each of the two stars, we use \project{emcee}
(\citealt{Foreman-Mackey:2013}) to generate posterior samples in $(r, v_\alpha,
v_\delta, \hat{v}_r)$ by running 64 walkers for 4608 steps and discarding the
first 512 steps as the burn-in period.
For each sample, we convert the heliocentric phase-space coordinates into
Galactocentric coordinates assuming the Sun's position and velocity are $x_\odot
= (-8.3, 0, 0)~{\rm kpc}$ and $v_\odot = (10, 244, 7.17)~\kms$ (\citealt{bovy,
etc.}).
\figname~\ref{fig:dxdv} shows differences in posterior samples converted to
Galactocentric phase-space coordinates for the two stars.
In all components, the pair is consistent with being co-moving and close in
separation; the sky-projected separation of the two stars is $\approx$$0.01~\pc$
but the median 3-space separation is $\approx$$0.6~\pc$.

@@

% ----------------
% Horizontal table
% ----------------
% \begin{table*}[htpb]
%   \centering
%   \caption{Astrometric and spectroscopic measurements}
%   \label{tab:t1}
%   \begin{tabular}{cccccccccc}
% \hline\hline
% Name & Sp Type & $T_\mathrm{eff}$ & $\log{g}$ & $v\sin{i}$ & $[\elem{Fe}/\elem{H}]$ & $v_r$ &
% $\varpi$ & $\mu_\alpha^*$ & $\mu_\delta$ \\
% % units
% \hline
% HD 240429 & G2 & 5878 & 4.43 & 1.1 & 0.01 & $-21.2$  & $9.35 \pm 0.24$ & $89.25 \pm 0.66$ & $-29.68 \pm 0.54$\\
% HD 240430 & G0 & 5803 & 4.33 & 2.5 & 0.20 & $-21.2$  & $9.41 \pm 0.25$ & $89.41 \pm 0.69$ & $-30.12 \pm 0.52$\\
% \hline\hline
% \end{tabular}
% \end{table*}

\begin{table*}[htpb]
  \caption{Astrometric and spectroscopic measurements.}
  \label{tab:t2}
  \begin{threeparttable}
  \centering
  \begin{tabular}{ccc}
\hline\hline
Name & HD 240429 & HD 240430 \\
\hline
Sp Type                                   & G2                & G0                \\
$T_\mathrm{eff}$                          & 5878              & 5803              \\
$\log{g}$                                 & 4.43              & 4.33              \\
$v\sin{i}$                                & 1.1               & 2.5               \\
$[\elem{Fe}/\elem{H}]$                    & 0.01              & 0.20              \\
$v_r$                                     & $-21.2$           & $-21.2$           \\
$\varpi$ \footnotemark[1]                 & $9.35 \pm 0.24$   & $9.41 \pm 0.25$   \\
$\mu_\alpha^*$ \footnotemark[1]           & $89.25 \pm 0.66$  & $89.41 \pm 0.69$  \\
$\mu_\delta$ \footnotemark[1]             & $-29.68 \pm 0.54$ & $-30.12 \pm 0.52$ \\
\hline
\multicolumn{3}{c}{$T_c < 1200$~K} \\
\hline
$A(\elem{Li})$ \footnotemark[2]           & $2.25$            & $2.75$            \\
$\elemH{C}$                               & $0.00$            & $0.09$            \\
$\elemH{N}$                               & $-0.06$           & $-0.01$           \\
$\elemH{O}$                               & $0.01$            & $0.09$            \\
$\elemH{Na}$                              & $-0.06$           & $-0.04$           \\
$\elemH{Mn}$                              & $-0.03$           & $0.00$            \\
\hline
\multicolumn{3}{c}{$T_c > 1200$~K} \\
\hline
$\elemH{Mg}$                              & $0.01$            & $0.19$            \\
$\elemH{Al}$                              & $0.01$            & $0.21$            \\
$\elemH{Si}$                              & $0.00$            & $0.16$            \\
$\elemH{Ca}$                              & $0.02$            & $0.23$            \\
$\elemH{Ti}$                              & $0.02$            & $0.20$            \\
$\elemH{V}$                               & $0.02$            & $0.20$            \\
$\elemH{Cr}$                              & $0.01$            & $0.17$            \\
$\elemH{Fe}$                              & $0.01$            & $0.20$            \\
$\elemH{Ni}$                              & $-0.01$           & $0.21$            \\
$\elemH{Y}$                               & $0.04$            & $0.26$            \\
\hline\hline
\end{tabular}
%
\begin{tablenotes}
  \item All spectroscopic measurements except $\elem{Li}$ are from \citealt{2016ApJS..225...32B}.
  \footnotetext[1]{From \tgas. }
  \footnotetext[2]{Absolute abundance from \todo{CITE}.}
\end{tablenotes}
  \end{threeparttable}
\end{table*}

@@

In fact, the surface lithium abundance is the only indication that points to younger ages.
If the two stars are indeed only several hundred Myrs old at most,
they are expected to be part of a larger co-moving group of stars.
However, as we mention above, there is no evidence in our search of co-moving pairs
using \tgas\ that the two stars belong to a larger group of young stars.
Very young stars are often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks.
We have looked for these signs for the pair to find none, and their spectral energy
distribution is consistent with blackbody.
The low $v\sin(i)$ values also argue against very young ages inferred from the
surface lithium abundances.
% TODO: ref for vertical action as age?
Finally, their fiducial orbit in a Milky Way-like potential show that the vertical action
for this pair is larger than the Sun, favoring an older age.
We concluded that the two stars are most likely coeval, $\sim 4$~Gyr old main sequence
stars, and that their unusually high \elem{Li} abundance requires an alternative explanation.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{abundances.pdf}
  \caption{Abundances of the co-moving pair, \sunanalog\ and \bizarreone.}
  \label{fig:abundances}
\end{figure}

@@

% chance pair
Given that their metallicities and abundance patterns are significantly
different, one may simply conclude that the two stars are not related (coeval)
but they merely happen to be co-moving at such small separation ($\approx 0.6$~pc)
by chance.
The two stars are in the Galactic disk, and assuming certain velocity ellipsoid
at the stars' location, one may compute the probability that a star moving at
the mean velocity of the two stars would have a companion within $\Delta v = XX$~km/s.
...

@@

The element \elem{Li} is worth a special attention in the context of accretion scenario.
Because Li is present in either carbonaceous chondrites or the bulk Earth with
a concentration of $1-1.5$~ppm in mass (\citealt{mcdonough2001composition,}),
but is depleted over time on the surface of a Sun-like star, accretion of
either at later time will significantly replenish the lithium on the star's
surface.
For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
material results in $\Delta\elemH{Li} \approx 1.6$~dex.
Incidentally, the star under examination, \bizarreone, has an age (informed by
stellar parameters) very close to the Sun ().
Thus, as long as we believe the Sun's present-day surface Li abundance
to be ordinary, this predicts that the \bizarreone\ should have $1.6$~dex enhancement
in its Li.
This is in fact exactly what we find: the Li abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t2}, \todo{CITE JM?})
approximately $1.6$~dex higher than the solar value of $1.1$~dex.
Furthermore, this implies that the accretion event should have happened
very recently from a time ago that is shorter than the \elem{Li} depletion time.

It is further worth pointing out that measuring the \elem{Li} abundance
with some of the refractory elements such as $\elem{Fe}$
provides a way to estimate the time of the event.
%exlain

@@

{\bf WASP-94A/WASP-94B:} 
\citealt{Teske:2016aa} studied WASP-94A/WASP-94B, a pair of F8 and F9 stars
with super-solar metallicity ($\feh\approx 0.3$ for both stars). Both stars
host a hot Jupiter.
The planet hosted by WASP-94A is transiting with a misaligned, probably
retrograde circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little
more massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host
star.
With a claimed precision of $0.006$~dex (median among all elements), they
detected a depletion of volatile and moderately volatile ($\Tcondens < 1200$~K)
elements at $0.02$~dex level and an enhancement in refractory ($\Tcondens >
1200$~K) elements at $0.01$~dex level in WASP-94A relative to WASP-94B.
Excluding K, which is based on one strong line and largely affected by non-LTE
effect, their analysis shows a statistically significant non-zero slope between
$\Delta\elemH{X}$ and $\Tcondens$\footnote{Note that the condensation
  temperature $\Tcondens$ used is for solar (system? atmosphere?) composition
  gas, which can differ from that of higher metallicity gas.}.
They considered multiple possibilities related to the formation and evolution
of planetary systems around each star as well as causes unrelated to planets
such as dust cleansing during the fully convective phase or different rotation
and granulation between the stars, but did not favor any particular one.

@@

% Useful follow up efforts

>>>>

\author{
  Semyeong Oh\altaffilmark{\pu,\lead},
  APW, JMB, KH, NL, DWH, DNS \etal\
}

@@

\begin{abstract}
  We report and discuss the discovery of a comoving pair of bright solar-type
  stars, \sunanalog\ and \bizarreone\, with significant differences in their chemical
  abundance patterns.
  The two stars are co-spatial ($|\Delta \bs{x}| < XX~\pc$) at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocities
  ($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence), as inferred from \gaia\
  \tgas\ proper motions and high resolution radial velocity measurements.
  Both stars are young with ages $\approx$$500~{\rm Myr}$ as estimated from
  their lithium abundances, favoring the idea that they were born together and
  are or were recently a bound, wide binary system.
  However, the metallicities and chemical abundances of refractory
  elements in the two stars are very different, challenging this simple picture.
  In order to reconcile the seemingly contradictory observations,
  we consider scenarios in which the pair is unrelated despite
  its current spatial and kinematic configuration, and
  those in which the pair formed together but may now have different chemistry.
  In the latter, we consider the possibility that the more metal-rich of the two,
  \bizarreone, accreted $\approx$10's of Earth masses of protoplanetary, rocky material,
  selectively enhancing the refractory elements.
  Direct-imaging and precision radial velocity follow-up to study the existence
  or properties of planetary systems around these stars would help distinguish
  these scenarios.
\end{abstract}

@@

Here, we report and discuss the discovery of a comoving pair of solar twin stars,
HD~240430 and HD~240429, with unusual chemical abundance and differential abundance patterns
that strongly suggest a dramatic accretion of planetary material by the two stars.
We nickname the two stars \bizarreone\ (HD~240430) and
\sunanalog\ (HD~240429) throughout the \documentname.
\todo{section summary}

@@

\input{kk.tex}

Though previously recognized as a visual double star system
(\citealt{2001AJ....122.3466M}), \sunanalog\ and \bizarreone\ were identified as a
candidate comoving star pair in our recent search for comoving stars using the
proper motions and parallaxes from the \tgas catalog, a component of \gaia\ \dr\
(the astrometric measurements are listed in \tablename~\ref{tab:kk}).
We refer the readers to this previous work (\citealt{2016arXiv161202440O}) for a
full explanation of the methodology behind this search and only briefly describe
the method here.
For a given pair, we compute a marginalized likelihood ratio between the
hypotheses (1) that a given pair of stars share the same 3D velocity vector, and
(2) that they have independent 3D velocity vectors, both given only observations
of two components of the velocities (proper motions).
We then select a sample of high-confidence comoving star pairs by making a
conservative cut on this likelihood ratio.
In the resulting catalog of comoving pairs (\citealt{2016arXiv161202440O}),
the pair presented in this paper was assigned a group id of 1199,
and the marginalized likelihood ratio (Bayes factor)
between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
well above the adopted cut value of 6.
We have checked that we do not find any possible additional comoving companions
by lowering the likelihood ratio cut for the stars around this pair.

In a separate effort to study detailed chemical abundances of
potential planet-hosting stars, \citet{2016ApJS..225...32B}
analyzed high resolution spectra of both stars obtained using HIRES spectrograph
on Keck~I telescope.
The spectral resolution is \todo{$R\approx XXX$} and the wavelength coverage is \todo{$XXX-XXX$~\AA}.
The resulting measurements include abundances measured for 15
chemical species (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as
well as high precision radial velocities.
Other stellar parameters derived from these spectra are included in
\tablename~\ref{tab:kk}.

Combining these precise radial velocities with the \gaia\ astrometry, we can
compare differences between the inferred 6D phase-space properties for the
two stars.
We start by generating posterior samples over the Heliocentric distance, $r$,
tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $\hat{v}_r$,
given the observed parallax, $\pi$, and proper motion components,
$(\mu_{\alpha^*}, \mu_\delta)$, and radial velocity, $v_r$.
By defining the vectors
% SMOH: I understand you meant hat v_r as the latent true radial velocity but
% personally think a) it can confuse some people that there are hat quantities
% with no-hat quantities for hat-y vector and thus b) it'd be better to use hat
% quantities for observed variables and no-hat for latent true ones.
% SMOH: v_r is missing in the LHS of eq(3)
\begin{eqnarray}
  \vec{y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          \pi &
          \mu_{\alpha^*} &
          \mu_\delta &
          v_r
        \end{array}
      \right)}\\
  \hat{\vec{y}} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          r^{-1} &
          r^{-1}\,v_\alpha &
          r^{-1}\,v_\delta &
          \hat{v}_r
        \end{array}
      \right)}
\end{eqnarray}
and by considering the covariance matrix $\mat{C}$ between the observed
quantities (provided by \tgas\ and extended to include the uncorrelated radial
velocity uncertainty), the likelihood can be written
\begin{eqnarray}
p(\pi, \mu_{\alpha^*}, \mu_\delta \given r, v_\alpha, v_\delta) &=&
  \left[\det\left(\frac{\mat{C}^{-1}}{2\pi}\right)\right]^{1/2} \,
    \exp \left[ -\frac{1}{2} \transp{\left(\vec{y} - \hat{\vec{y}} \right)} \,
    \mat{C}^{-1} \,
    \left(\vec{y} - \hat{\vec{y}} \right) \right] \label{eq:likefn} \quad .
\end{eqnarray}
We adopt a uniform space density prior for the distance and an isotropic
Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
\begin{eqnarray}
p(r) &=&
  \begin{cases}
    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
    0              & \text{otherwise}
  \end{cases}\\
p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
\end{eqnarray}
For each of the two stars, we use \project{emcee}
(\citealt{Foreman-Mackey:2013}) to generate posterior samples in $(r, v_\alpha,
v_\delta, \hat{v}_r)$ by running 64 walkers for 4608 steps and discarding the
first 512 steps as the burn-in period.
For each sample, we convert the heliocentric phase-space coordinates into
Galactocentric coordinates assuming the Sun's position and velocity are $x_\odot
= (-8.3, 0, 0)~{\rm kpc}$ and $v_\odot = (10, 244, 7.17)~\kms$ (\citealt{bovy,
etc.}).
\figname~\ref{fig:dxdv} shows differences in posterior samples converted to
Galactocentric phase-space coordinates for the two stars.
In all components, the pair is consistent with being comoving and close in
separation; the sky-projected separation of the two stars is $\approx$$0.01~\pc$
but the median 3-space separation is $\approx$$0.6~\pc$.

@@

@@

In fact, the surface lithium abundance is the only indication that points to younger ages.
If the two stars are indeed only several hundred Myrs old at most,
they are expected to be part of a larger comoving group of stars.
However, as we mention above, there is no evidence in our search of comoving pairs
using \tgas\ that the two stars belong to a larger group of young stars.
Very young stars are often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks.
We have looked for these signs for the pair to find none, and their spectral energy
distribution is consistent with blackbody.
The low $v\sin(i)$ values also argue against very young ages inferred from the
surface lithium abundances.
% TODO: ref for vertical action as age?
Finally, their fiducial orbit in a Milky Way-like potential show that the vertical action
for this pair is larger than the Sun, favoring an older age.
We concluded that the two stars are most likely coeval, $\sim 4$~Gyr old main sequence
stars, and that their unusually high \elem{Li} abundance requires an alternative explanation.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{abundances.pdf}
  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone.}
  \label{fig:abundances}
\end{figure}

@@

% chance pair
Given that their metallicities and abundance patterns are significantly
different, one may simply conclude that the two stars are not related (coeval)
but they merely happen to be comoving at such small separation ($\approx 0.6$~pc)
by chance.
The two stars are in the Galactic disk, and assuming certain velocity ellipsoid
at the stars' location, one may compute the probability that a star moving at
the mean velocity of the two stars would have a companion within $\Delta v = XX$~km/s.
...

@@

The element \elem{Li} is worth a special attention in the context of accretion scenario.
Because Li is present in either carbonaceous chondrites or the bulk Earth with
a concentration of $1-1.5$~ppm in mass (\citealt{mcdonough2001composition,}),
but is depleted over time on the surface of a Sun-like star, accretion of
either at later time will significantly replenish the lithium on the star's
surface.
For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
material results in $\Delta\elemH{Li} \approx 1.6$~dex.
Incidentally, the star under examination, \bizarreone, has an age (informed by
stellar parameters) very close to the Sun ().
Thus, as long as we believe the Sun's present-day surface Li abundance
to be ordinary, this predicts that the \bizarreone\ should have $1.6$~dex enhancement
in its Li.
This is in fact exactly what we find: the Li abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \todo{CITE JM?})
approximately $1.6$~dex higher than the solar value of $1.1$~dex.
Furthermore, this implies that the accretion event should have happened
very recently from a time ago that is shorter than the \elem{Li} depletion time.

It is further worth pointing out that measuring the \elem{Li} abundance
with some of the refractory elements such as $\elem{Fe}$
provides a way to estimate the time of the event.
If the observed \elem{Li} abundance is less than what is inferred from
abundance differences of other elements, and
we have a model of \elem{Li} depletion, the time of \elem{Li} enhancement
may be calculated.

What about \sunanalog?
\sunanalog\ is also enhanced in \elem{Li} considering its age of $4.00_{-1.56}^{+1.51}$~Gyr
than the nominal \elem{Li} depletion predics by $\approx 1$~dex.
This enhancement puts an upper limit on the accreted mass to be \todo{$\approx 4$~\mearth}
assuming \elem{Li} concentration of $1.1$~ppm (\citealt{mcdonough2001composition}).
Unlike \bizarreone, we cannot know the pre-accretion abundances of \sunanalog.
However, we note that the span of abundance difference between highly volatile elements
(C, N, O, Na) and refractory elements such as \elem{Fe} expected from accreting
\todo{$\approx 4$~\mearth} to the Sun is $\approx 0.05$~dex.
This is comparable to the abundance difference between N, Na and Fe in \sunanalog.
It is also interesting that \sunanalog\ also shows a deficit in the same
volatile and moderately volatile elements (C, N, O, Na, and Mn) relative to Fe
just as in \bizarreone.
Thus, we conclude that \sunanalog\ is also likely to have had a similar
accretion event, but the amount of accretion was much smaller than \bizarreone.

We stress that
% - these calculations are carried out with very simple and unverified assumptions
% - uncertainties exist on the bulk Earth

@@

{\bf WASP-94A/WASP-94B:} 
\citealt{Teske:2016aa} studied WASP-94A/WASP-94B, a pair of F8 and F9 stars
with super-solar metallicity ($\feh\approx 0.3$ for both stars). Both stars
host a hot Jupiter.
The planet hosted by WASP-94A is transiting with a misaligned, probably
retrograde circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little
more massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host
star.
With a claimed median uncertainty of $0.006$~dex among all elements, they
detected a depletion of volatile and moderately volatile ($\Tcondens < 1200$~K)
elements at $0.02$~dex level and an enhancement in refractory ($\Tcondens >
1200$~K) elements at $0.01$~dex level in WASP-94A relative to WASP-94B.
Excluding K, which is based on one strong line and largely affected by non-LTE
effect, their analysis shows a statistically significant non-zero slope between
$\Delta\elemH{X}$ and $\Tcondens$\footnote{Note that the condensation
  temperature $\Tcondens$ used is for solar (system? atmosphere?) composition
  gas, which can differ from that of higher metallicity gas.}.
They considered multiple possibilities related to the formation and evolution
of planetary systems around each star as well as causes unrelated to planets
such as dust cleansing during the fully convective phase or different rotation
and granulation between the stars, but did not favor any particular one.

@@

% Useful follow up efforts
We discuss the follow up efforts that would be useful to further
illuminate the peculiar abundance difference between the pair.

\section{Summary}
\label{sec:summary}

We have reported and discussed the discovery of a comoving pair of bright solar-type stars
HD~240430 and HD~240429 (G0 and G2)
with very different metallicity ($\Delta\feh \approx 0.2$~dex),
and a condensation temperature-dependent abundance difference.
